---
title: "Test"
author: "Witsch Daniel"
date: "11 April 2016"
output:
  beamer_presentation: default
header-includes: 
  - \usepackage{tikz}
  - \usepackage{pgfplots}
params:
  input : !r c(1,1,1,0,0,0)
  output : !r c(1,1,1,1,1,1,1,1)
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

## Parameter

```{r, results='asis'}
for(i in c(1:3)){
  pandoc.header("jakldf")
}
params$input
```

# Parameter 2
```{r}
params$output
hallo()
```

# Tabelle 1

```{r, results='asis'}
pandoc.table(head(iris[,1:3]))
```

# Tabelle 2

```{r}
knitr::kable(head(iris[,1:3]), format = "markdown")
```

## Tikz

\begin{tikzpicture}
\begin{axis}[xmax=9,ymax=9, samples=50]
  \addplot[blue, ultra thick] (x,x*x);
  \addplot[red,  ultra thick] (x*x,x);
\end{axis}
\end{tikzpicture}




