---
title: "Test"
author: "Witsch Daniel"
date: "11 April 2016"
output:
  beamer_presentation:
    keep_tex: yes
  ioslides_presentation: default
params:
  input: c(1,1,1,0,0,0)
  output: c(1,1,1,1,1,1,1,1)
header-includes:
- \usepackage{tikz}
- \usepackage{pgfplots}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

```{r, results='asis'}
for(i in c(1:3)){
  pander::pandoc.header("jakldf")
  params$input
}
```

## Parameter 2

```{r}
params$output
```

## Tabelle 1

```{r, results='asis'}
pander::pandoc.table(head(iris[,1:3]))
```

## Tabelle 2

```{r}
knitr::kable(head(iris[,1:3]), format = "markdown")
```

## Tikz

\begin{tikzpicture}
\begin{axis}[xmax=`r 3`,ymax=`r 5`, samples=50]
  \addplot[blue, ultra thick] (x,x*x);
  \addplot[red,  ultra thick] (x*x,x);
\end{axis}
\end{tikzpicture}

## Tikz 2

\begin{tikzpicture}
\draw[style=dashed] (2,.5) circle (0.5);
\draw[fill=green!50] (1,1)
ellipse (.5 and 1);
\draw[fill=blue] (0,0) rectangle (1,1);
\draw[style=thick]
(3,.5) -- +(30:1) arc(30:80:1) -- cycle;
\end{tikzpicture}

## Tikz 3

\usetikzlibrary{backgrounds}
\vspace*{-2.3cm}\hspace{8cm}%
\begin{tikzpicture}[ scale=.8, show background rectangle]
\draw (2,2) circle (1);
\draw (1 mm, 10 pt) -- (4 em, 1);
\end{tikzpicture}

## Tikz 4

\begin{tikzpicture}[ scale=.8]
\draw (2,2) circle (1);
\draw (1 mm, 10 pt) -- (4 em, 1);
\end{tikzpicture}

## Tikz 5

\begin{tikzpicture}
\path[clip, draw] (1,1)--(2,2)--(3,1)--cycle;
\path[fill=blue!50] (2, 1.7) circle (.8);
\end{tikzpicture}

## Tikz 6

\begin{tikzpicture}
\path[draw] (1,1)--(2,2)--(3,1)--cycle;
\path[fill=blue!50] (2, 1.7) circle (.8);
\end{tikzpicture}

## Tikz 7

\begin{tikzpicture}
\draw (0, 0) rectangle (7, 5);
\draw (3, 1) rectangle (1, 3);
\draw (3, 3) rectangle (1, 3);
\end{tikzpicture}









