---
title: "Faltungskode Dekodierung"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: beamer_presentation
fontsize: 8pt
params:
  conv.encoder: !r list(N=2, M=2, generators=c(7,5), rsc=FALSE, termination=logical(0), next.state=matrix(c(0,0,1,1,2,2,3,3), ncol =2), prev.state=matrix(c(0,2,-1,-1,-1,-1,0,2,1,3,1,3), ncol =3), output=matrix(c(0,3,2,1,3,0,1,2), ncol =2))
  code: !r c(-3.0409, -1.3420, -0.2564,  2.6875, -0.3180, 1.1115, 0.5514, 0.8717, -1.1767, -1.0351)
  decoded: !r c(1,0,1,0,0)
  trellis: !r matrix(c(0,NA,NA,NA,-2,NA,2,NA,-2,4,-2,0,2,0,6,0,2,8,NA,NA,10,NA,NA,NA), nrow = 4)
  survivor.states: !r matrix(c(0,0,0,0,0,3,0,3,0,2,0,2,1,3,1,3,0,2,0,2,1,3,1,3), nrow = 4)
  soft.flag: !r TRUE
header-includes:
- \usepackage{tikz}
- \usepackage{pgfplots}
- \usepackage{mathtools}
- \usetikzlibrary{arrows,decorations.pathmorphing,backgrounds,positioning,fit,petri,calc}
---

```{r, include=FALSE}
# transforms an integer value n to a at least min.length bit binary vector
binVector <- function(n, min.length) {

  result <- integer()
  i <- 0
  while (n != 0) {
    result <- c(n %% 2, result)
    n = n %/% 2
    i <- i + 1
  }

  zeros <- rep(0, times = min.length)

  result <- c(zeros, result)

  return(tail(result,min.length))
}

# returns an ordering of the state numbers for a nice state diagram
ordering <- function(num.states, next.state) {
  #next.state <- matrix(rep(0:(num.states-1), each = 2), ncol = 2)
  result <- integer(1)

  n <- 0
  for (i in 2:num.states) {
    n0 <- next.state[n+1,1]
    n1 <- next.state[n+1,2]

    if (n0 %in% result) {
      n <- n1
    }
    else if (n1 %in% result) {
      n <- n0
    }
    else {
      n <- if (n0 > n1) n0 else n1
    }

    result <- c(result, n)
  }

  return(result)
}

decToBin <- function(x) { if (all(x<2)) x else paste(decToBin(x%/%2), x%%2, sep="") }

octalToDec <- function(x) {
  res <- numeric()
  for(j in 1:length(x)) {
  dec <- 0
  i <- 0
    while (x[j] > 0) {
      dec <- dec + (x[j] %% 10) * (8^i)
      i <- i + 1
      x[j] <- x[j] %/% 10
    }
  res[j] <- dec
  }

  return(res)
}
```

```{r, include=FALSE}
conv.encoder <- params$conv.encoder

M <- conv.encoder$M
N <- conv.encoder$N
generators <- conv.encoder$generators
output <- conv.encoder$output
next.state <- conv.encoder$next.state
prev.state <- conv.encoder$prev.state
rsc.flag <- conv.encoder$rsc
decoded <- params$decoded
trellis <- params$trellis
survivor.states <- params$survivor.states

num.states <- 2^M

if (num.states > 4) {
  yfactor = 0.75
} else {
  yfactor = 1.25
}

if (ncol(trellis) > 10) {
  xfactor = max(0.73, exp((10-ncol(trellis))/13))
} else {
  xfactor = 1
}


tikz.trellis <- ""

## TRELLIS DIAGRAM
# trellis nodes
for (t in 1:ncol(trellis)) {
  for (s in 1:num.states) {

    if (is.na(trellis[s,t])) {
      nodetype <- "freestate"
      value <- ""
    }
    else {
      nodetype <- "state"
      value <- trellis[s,t]
    }
    definition <- paste0("\\node[",nodetype,"]")
    nodename <- paste0("(node",s-1,t-1,")")
    coordinate <- paste0("at (",xfactor*(t-1),",",yfactor*(-s+1),")")
    label <- paste0("{",value,"}")
    single.node <- paste(definition,nodename,coordinate,label,";")

    tikz.trellis <- paste(tikz.trellis, single.node)
  }
}

# state labels
for (s in 0:(num.states-1)) {
  value <- paste(binVector(s,M),collapse = "")
  label <- paste0("\\node (statelabel",s,") [left of=node",s,"0, xshift=4mm] {",value,"};")

  tikz.trellis <- paste(tikz.trellis, label)
}

# decoded message under trellis diagram
for (t in 0:(length(decoded)-1)) {
  max.state <- num.states - 1
  visibility <- paste0("\\visible<",ncol(trellis)+1,">")
  position <- paste0("($(node",max.state,t,")!0.5!(node",max.state,t+1,")+(0,-.5)$)")
  decoded.bit <- paste0(visibility,"{\\node [orange, font=\\small] at",position," {",decoded[t+1],"};}")
  
  tikz.trellis <- paste(tikz.trellis, decoded.bit)
}

# output label
visibility <- paste0("\\visible<",ncol(trellis)+1,">")
position <- paste0("below=.54 of statelabel",num.states - 1,".west, anchor=west")
output.label <- paste0(visibility,"{\\node [orange, font=\\small,",position,"] (outlabel) {output:};}")
tikz.trellis <- paste(tikz.trellis, output.label)

# bit legend
legend.bit.0 <- "\\draw [->] ($(outlabel.west)+(0,-1)$) -- ++(1,0) node (bit0) [right] {Bit 0};"
legend.bit.1 <- "\\draw [->, dashed] ($(bit0.east)+(.5,0)$) -- ++(1,0) node (bit1) [right] {Bit 1};"
tikz.trellis <- paste(tikz.trellis, legend.bit.0, legend.bit.1)

# time labels
for (t in 0:(ncol(trellis)-1)) {
  label <- paste0("\\node (timelabel",t,") [above of=node0",t,", yshift=-4mm] {",t,"};")

  tikz.trellis <- paste(tikz.trellis, label)
}

# node connections
x <- 0
for (t in 1:(ncol(trellis)-1)) {
  x.next <- next.state[x+1,decoded[t]+1]
  for (s in 0:(num.states-1)) {

    if (!is.na(trellis[s+1,t])) {
      this.node <- paste0("(node",s,t-1,")")

      if (!is.na(trellis[next.state[s+1,1]+1,t+1])) {
        next.node.0 <- paste0("(node",next.state[s+1,1],t,")")
        label.value.0 <- paste(binVector(output[s+1,1],N),collapse = "")
        label.0 <- paste0("node [sloped, above, very near start] {",label.value.0,"}")
        edge.0 <- paste("\\draw[->]",this.node,"--",next.node.0,label.0,";")
        
        if (s == x && x.next == next.state[s+1,1]) {
          # path of the decoded message will be colored
          color.edge <- paste("\\draw[->, orange]",this.node,"--",next.node.0,label.0,";")
          edge.0 <- paste0("\\alt<",ncol(trellis)+2-t,"-> {",color.edge,"}{",edge.0,"};")
        }
        else if (survivor.states[next.state[s+1,1]+1,t+1] != s) {
          # remove non-survivor paths at the end
          # edge.0 <- paste("\\alt<-",ncol(trellis),"> {",edge.0,"}{};")
          edge.0 <- paste("\\alt<1> {",edge.0,"}{};")
        }

        tikz.trellis <- paste(tikz.trellis, edge.0)
      }

      if (!is.na(trellis[next.state[s+1,2]+1,t+1])) {
        next.node.1 <- paste0("(node",next.state[s+1,2],t,")")
        label.value.1 <- paste(binVector(output[s+1,2],N),collapse = "")
        label.1 <- paste0("node [sloped, above, very near start] {",label.value.1,"}")
        edge.1 <- paste("\\draw[->, dashed]",this.node,"--",next.node.1,label.1,";")
        
        if (s == x && x.next == next.state[s+1,2]) {
          # path of the decoded message will be colored
          color.edge <- paste("\\draw[->, dashed, orange]",this.node,"--",next.node.1,label.1,";")
          edge.1 <- paste0("\\alt<",ncol(trellis)+2-t,"-> {",color.edge,"}{",edge.1,"};")
        }
        else if (survivor.states[next.state[s+1,2]+1,t+1] != s) {
          # remove non-survivor paths at the end
          # edge.1 <- paste("\\alt<-",ncol(trellis),"> {",edge.1,"}{};")
          edge.1 <- paste("\\alt<1> {",edge.1,"}{};")
        }

        tikz.trellis <- paste(tikz.trellis, edge.1)
      }
    }
  }
  x <- x.next
}
```

```{r, include=FALSE}
# Kodierer Informationen
if (rsc.flag == TRUE) {
  art.coder <- "Rekursiver"
} else {
  art.coder <- "Nicht-Rekursiver"
}

if (rsc.flag == FALSE) {
  generator.matrix <- paste0(decToBin(octalToDec(generators)), " \\\\ ", collapse = "")
  generator.print <- 
    paste0("(", paste(generators, collapse=","), ")_8 = \\begin{pmatrix}", generator.matrix, "\\end{pmatrix}")

} else {
  generator.print <- paste0("\\left(1,", paste0("\\frac{", head(generators, length(generators) - 1), "}{", tail(generators, 1), "}", collapse = ","), "\\right)")
}
```

## Kodierer Information

- `r art.coder` Kodierer
- Anzahl von Ausgängen : $$N=`r N`$$
- Anzahl von Registern : $$M=`r M`$$
- Generatoren : $$`r generator.print`$$
- Kode-Rate: $$\frac{1}{`r N`}$$

## Kodierer Matrix : Nächster Zustand
```{r, echo=FALSE, results='asis'}
next.table <- next.state
colnames(next.table) <- c("Bit 0", "Bit 1")
row.counter <- rep(0:(dim(next.table)[1]-1))
rownames(next.table) <- paste("Zustand ", row.counter)
#knitr::kable(next.table, format="latex", align="c")
```

## Kodierer Matrix : Ausgangsbits
```{r, echo=FALSE, results='asis'}
output.table <- output
output.table <- matrix(decToBin(as.vector(output.table)), ncol = ncol(output.table))
colnames(output.table) <- c("Bit 0", "Bit 1")
row.counter <- rep(0:(dim(next.table)[1]-1))
rownames(output.table) <- paste("Zustand ", row.counter)
#knitr::kable(output.table, format="latex", align="c")
```

## Input: Signal zu Kode

Signal: (`r round(params$code, digits = 1)`)
\vspace*{10mm}
\begin{equation*}
  \text{Kode(signal)} =
  \begin{cases}
    0  & \quad \text{wenn signal } \geq 0\\
    1  & \quad \text{sonst}\\
  \end{cases}
\end{equation*}
\vspace*{10mm}
Kode: (`r ifelse(params$code >= 0, 0, 1)`)

## Trellis Diagramm `r if(params$soft.flag) "(soft decision)" else "(hard decision)"`

input: (`r ifelse(params$code >= 0, 0, 1)`)
\vfill
\begin{tikzpicture}[>=stealth, font=\tiny]
\tikzstyle{state} = [draw, circle, teal, thick, text=black, minimum size=3.5mm, inner sep=0mm]
\tikzstyle{freestate} = [circle, teal, fill=teal, minimum size=1mm, inner sep=0mm]

`r tikz.trellis`

\end{tikzpicture}
