---
title: "Convolution"
output: 
  beamer_presentation:
    keep_tex: true
author: Martin Nocker
fontsize: 9pt
params:
  conv.encoder: !r list(N=2, M=2, generators=c(7,5), rsc=FALSE, termination=logical(0), next.state=matrix(c(0,0,1,1,2,2,3,3), ncol =2), prev.state=matrix(c(0,2,-1,-1,-1,-1,0,2,1,3,1,3), ncol =3), output=matrix(c(0,3,2,1,3,0,1,2), ncol =2))
  message: !r c(1,0,1)
  terminate: !r TRUE
header-includes:
- \usepackage{tikz}
- \usepackage{pgfplots}
- \usepackage{mathtools}
- \usetikzlibrary{arrows,decorations.pathmorphing,backgrounds,positioning,fit,petri,calc}
---

```{r, include=FALSE}
# transforms an integer value n to a at least min.length bit binary vector
binVector <- function(n, min.length) {

  result <- integer()
  i <- 0
  while (n != 0) {
    result <- c(n %% 2, result)
    n = n %/% 2
    i <- i + 1
  }

  zeros <- rep(0, times = min.length)

  result <- c(zeros, result)

  return(tail(result,min.length))
}

# returns an ordering of the state numbers for a nice state diagram
ordering <- function(num.states, next.state) {
  #next.state <- matrix(rep(0:(num.states-1), each = 2), ncol = 2)
  result <- integer(1)

  n <- 0
  for (i in 2:num.states) {
    n0 <- next.state[n+1,1]
    n1 <- next.state[n+1,2]

    if (n0 %in% result) {
      n <- n1
    }
    else if (n1 %in% result) {
      n <- n0
    }
    else {
      n <- if (n0 > n1) n0 else n1
    }

    result <- c(result, n)
  }

  return(result)
}
```

```{r, include=FALSE}
conv.encoder <- params$conv.encoder

message <- params$message

M <- conv.encoder$M
N <- conv.encoder$N
output <- conv.encoder$output
next.state <- conv.encoder$next.state
prev.state <- conv.encoder$prev.state
termination <- conv.encoder$termination
rsc.flag <- conv.encoder$rsc
terminate <- params$terminate

num.states <- 2^M

matrix.length <- num.states * (length(message) + as.integer(terminate)*M)
state.color.matrix <- matrix(rep(NA,matrix.length), ncol = num.states)
s <- 0
for (i in 1:(matrix.length/num.states)) {
  state.color.matrix[i,s+1] <- i+1
  if (i > length(message)) {
    bit <- if(rsc.flag) termination[s+1] else 0
  } else {
    bit <- message[i]
  }
  s <- next.state[s+1,bit+1]
}

state.order <- ordering(num.states, next.state)

## STATE DIAGRAM
tikz.diagram <- ""
# state diagram nodes
for (s in 0:(num.states-1)) {
  color.frames <- state.color.matrix[,state.order[s+1]+1]
  color.frames <- paste(color.frames[!is.na(color.frames)], collapse = ",")
  color.frames <- if(color.frames == "") 0 else color.frames
  
  xpos <- 2.5*sin(s*2*pi/num.states)
  ypos <- 2.5*cos(s*2*pi/num.states)
  position <- paste0(xpos,",",ypos)
  name <- paste(binVector(state.order[s+1],M),collapse = "")
  black.state <- paste0("\\node[state] (state",state.order[s+1],") at (",position,") {",name,"};")
  
  color.state <- paste0("\\node[state, orange] (state",state.order[s+1],") at (",position,") {",name,"};")
  
  
  state <- paste0("\\alt<",color.frames,"> {",color.state,"}{",black.state,"};")

  tikz.diagram <- paste(tikz.diagram, state)
}

# state diagram connections
for (s in 0:(num.states-1)) {
  this.state <- paste0("(state",s,")")
  n_next.state.0 <- next.state[s+1,1]
  n_next.state.1 <- next.state[s+1,2]
  str_next.state.0 <- paste0("(state",n_next.state.0,")")
  str_next.state.1 <- paste0("(state",n_next.state.1,")")

  label.value.0 <- paste(binVector(output[s+1,1],N),collapse = "")
  label.value.1 <- paste(binVector(output[s+1,2],N),collapse = "")

  # indices of the states in the ordering vector (1 based)
  this.ordering.index <- which(state.order == s)
  next.0.ordering.index <- which(state.order == n_next.state.0)
  next.1.ordering.index <- which(state.order == n_next.state.1)

  # if edges do not go to neighbour, set label near start
  # to avoid label crossings
  near.0 <- ""
  near.1 <- ""
  distance.to.0 <- abs(this.ordering.index - next.0.ordering.index)
  distance.to.1 <- abs(this.ordering.index - next.1.ordering.index)
  if (distance.to.0 > 1 && distance.to.0 < num.states-1) {
    near.0 <- ",near start"
  }

  if (distance.to.1 > 1 && distance.to.1 < num.states-1) {
    near.1 <- ",near start"
  }
  # 2nd check in previous if clause necessary because if state numbers
  # are in first and last position of the ordering, they have distance
  # num.states-1 but are neighbours in the state diagram

  label.0 <- paste0("node [sloped, above",near.0,"] {",label.value.0,"}")
  label.1 <- paste0("node [sloped, above",near.1,"] {",label.value.1,"}")

  # in case of a loop
  angle <- (90-(this.ordering.index-1)*360/num.states) %% 360
  angle.out <- (angle + 15) %% 360
  angle.in <- (angle - 15) %% 360

  if (n_next.state.0 == s) {
    # loop with input bit 0
    loop <- paste0("[looseness=8,out=",angle.out,",in=",angle.in,"]")

    if (sin(angle*pi/180) < 0) {
      label.0 <- paste0("node [sloped, below",near.0,"] {",label.value.0,"}")
    }

    edge.0 <- paste("\\draw[->]",this.state,"to",loop,label.0,this.state,";")
  }
  else {
    # 'normal' edge to other node
    bend <- ""
    if (next.state[n_next.state.0+1,1] == s || next.state[n_next.state.0+1,2] == s) {
      # there is a connection back -> bend the edge
      bend <- "[bend left=15]"
    }
    edge.0 <- paste("\\draw[->]",this.state,"to",bend,label.0,str_next.state.0,";")
  }

  if (n_next.state.1 == s) {
    # loop with input bit 1
    loop <- paste0("[looseness=8,out=",angle.out,",in=",angle.in,"]")

    if (sin(angle*pi/180) < 0) {
      label.1 <- paste0("node [sloped, below",near.1,"] {",label.value.1,"}")
    }

    edge.1 <- paste("\\draw[->, dashed]",this.state,"to",loop,label.1,this.state,";")
  }
  else {
    # 'normal' edge to other node
    bend <- ""
    if (next.state[n_next.state.1+1,1] == s || next.state[n_next.state.1+1,2] == s) {
      # there is a connection back -> bend the edge
      bend <- "[bend left=15]"
    }
    edge.1 <- paste("\\draw[->, dashed]",this.state,"to",bend,label.1,str_next.state.1,";")
  }

  tikz.diagram <- paste(tikz.diagram, edge.0, edge.1)
}

## ENCODE TABLE
encode.table <- ""
index <- 2
state <- 0
for (i in message) {
  visibility <- paste0("\\visible<",index,"->")
  thisState <- paste(binVector(state,M),collapse = "")
  code.output <- paste(binVector(output[state+1,i+1],N),collapse = "")
  nextState <- paste(binVector(next.state[state+1,i+1],M),collapse = "")
  hline <- ""
  
  if (terminate && index == length(message) + 1) {
    hline <- "\\hline"
  }
  
  table.row <- paste(visibility,"{",thisState,"&",i,"&",code.output,"&",nextState,"\\\\",hline,"}")
  
  encode.table <- paste(encode.table, table.row)
  
  index <- index + 1
  state <- next.state[state+1,i+1]
}

# termination bits
if (terminate) {
  for (i in 1:M) {
    term.bit <- if(rsc.flag) termination[state+1] else 0
    
    visibility <- paste0("\\visible<",index,"->")
    thisState <- paste(binVector(state,M),collapse = "")
    code.output <- paste(binVector(output[state+1,term.bit+1],N),collapse = "")
    nextState <- paste(binVector(next.state[state+1,term.bit+1],M),collapse = "")
    
    table.row <- paste(visibility,"{",thisState,"&",term.bit,"&",code.output,"&",nextState,"\\\\ }")
    
    encode.table <- paste(encode.table, table.row)
  
    index <- index + 1
    state <- next.state[state+1,term.bit+1]
  }
}
```



## Convolution Encode

\begin{center}
\begin{minipage}{.45\textwidth}
\begin{center}
\begin{tabular}{c c c c}
  \visible<1-> {state&input&output&next state\\ \hline}
  `r encode.table`
\end{tabular}
\end{center}
\end{minipage}
\hfill
\begin{minipage}{.45\textwidth}
\begin{center}
\begin{tikzpicture}[scale=.70, >=stealth, font=\tiny]
\tikzstyle{state} = [draw, circle, inner sep=1mm, minimum size=6mm, font=\scriptsize]
`r tikz.diagram`
\end{tikzpicture}
\end{center}
\end{minipage}
\end{center}

## state color matrix

`r paste(state.color.matrix[,1][!is.na(state.color.matrix[,1])], collapse=",")`

`r paste(state.color.matrix[,2][!is.na(state.color.matrix[,2])], collapse=",")`

`r paste(state.color.matrix[,3][!is.na(state.color.matrix[,3])], collapse=",")`

`r paste(state.color.matrix[,4][!is.na(state.color.matrix[,4])], collapse=",")`
