---
title: "Simulation"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: beamer_presentation
params:
  turbo: !r TRUE
  message.length: !r 100
  iterations.per.db: !r 100
  min.db: !r 0.1
  max.db: !r 2.0
  db.interval: !r 0.1
  permutation: !r c(1,2,3,4,5,6,7)
  decode.iterations: !r 10
  punctuation: !r matrix(c(1,0,1,1,1,0), nrow = 3)
  encoder: !r list(N=2, M=2, generators=c(5,7,3,7), rsc=TRUE, termination=c(0,1,1,0), next.state=matrix(c(0,2,3,1,2,0,1,3), ncol =2), prev.state=matrix(c(0,3,1,2,1,2,0,3,-1,-1,-1,-1), ncol =3), output=matrix(c(0,0,1,1,3,3,2,2), ncol =2))
  dataframe: !r data.frame(ber=seq(from=0.01, to=0.001, length.out = 11), db=seq(from=0.5, to=2, length.out = 11))
header-includes:
- \usepackage{tikz}
- \usepackage{pgfplots}
- \usepackage{mathtools}
- \usetikzlibrary{arrows,decorations.pathmorphing,backgrounds,positioning,fit,petri,calc}
---

```{r, include=FALSE}
binVector <- function(n, min.length) {

  result <- integer()
  i <- 0
  while (n != 0) {
    result <- c(n %% 2, result)
    n = n %/% 2
    i <- i + 1
  }

  zeros <- rep(0, times = min.length)

  result <- c(zeros, result)

  return(paste(tail(result,min.length), collapse = ""))
}

decToBin <- function(x) { if (all(x<2)) x else paste(decToBin(x%/%2), x%%2, sep="") }

octalToDec <- function(x) {
  res <- numeric()
  for(j in 1:length(x)) {
  dec <- 0
  i <- 0
    while (x[j] > 0) {
      dec <- dec + (x[j] %% 10) * (8^i)
      i <- i + 1
      x[j] <- x[j] %/% 10
    }
  res[j] <- dec
  }

  return(res)
}

gcd <- function(n, m) {
  if (n == 0 && m == 0) return(0)
  
  n <- abs(n); m <- abs(m)
  if (m > n) {
    t <- n; n <- m; m <- t
  }
  while (m > 0) {
    t <- n
    n <- m
    m <- t %% m
  }
  return(n)
}
```

```{r, include=FALSE}
node.short <- 20
node.long <- 45
dots <- function (v, node) if(length(v) > node) ", ..." else ""

if (params$encoder$rsc == TRUE) {
  art.coder <- "Rekursiver"
} else {
  art.coder <- "Nicht-Rekursiver"
}

if (params$encoder$rsc == FALSE) {
  generator.matrix <- 
    paste0(decToBin(octalToDec(params$encoder$generators)), " \\\\ ", collapse = "")
  generator.print <- paste0("(", paste(params$encoder$generators, collapse=","), 
                           ")_8 = \\begin{pmatrix}", generator.matrix, "\\end{pmatrix}")

} else {
  generator.print <- 
    paste0("\\left(1,", 
           paste0("\\frac{", 
              head(params$encoder$generators, length(params$encoder$generators) - 1), "}{",
                        tail(params$encoder$generators, 1), "}", collapse = ","), "\\right)")
}


punctuation.print <- if(!is.null(params$punctuation)) paste0(apply(params$punctuation, 1, function(x) {paste0(x, collapse=" & ")}), collapse = " \\\\ ")
```

## Kodierer Information

- `r art.coder` Kodierer
- Anzahl von Ausgängen : $$N=`r params$encoder$N`$$
- Anzahl von Registern : $$M=`r params$encoder$M`$$
- Generatoren : $$`r generator.print`$$
`r if(params$turbo) paste0("- Turbo-Dekodierungsiterationen : ", params$decode.iterations)`

## Kodierer Information

```{r, include=FALSE}
if (is.null(params$punctuation)) {
  if (params$turbo) {
    code.rate <- "$$\\frac{1}{3}$$"
  } else {
    code.rate <- paste0("$$\\frac{1}{",params$encoder$N,"}$$")
  }
} else {
  factor <- 3
  if (!params$turbo) {
    factor <- params$encoder$N
  }
  
  gcd.value <- gcd(length(params$punctuation), sum(params$punctuation) * factor)
  
  code.rate <- paste0("$$\\frac{",length(params$punctuation) / gcd.value,"}{",sum(params$punctuation) * factor / gcd.value,"}$$")
}
```

- Kode-Rate : `r code.rate`
`r if(params$turbo) paste0("- Interleaver : (", paste(head(params$permutation, node.long), collapse = ", "), dots(params$permutation, node.long), ")") `
`r if(!is.null(params$punctuation)) paste0("- Punktierungs-Matrix : $$\\begin{pmatrix} ",punctuation.print," \\end{pmatrix}$$")`

## Simulationsdaten

- Nachrichtenlänge: `r params$message.length`
- Iterationen pro SNR: `r params$iterations.per.db`
- SNR Minimum: `r params$min.db`
- SNR Maximum: `r params$max.db`
- SNR Intervall: `r params$db.interval`

## Plot

```{r, echo=FALSE}

df <- params$dataframe
if (max(df$ber) == 0) {
  ggplot2::ggplot(df,ggplot2::aes(db))+ggplot2::geom_line(ggplot2::aes(y = ber))+ggplot2::xlab("Signal Rausch Verh\u00e4ltnis [dB]")+ggplot2::ylab("Bitfehlerrate")
} else {
  ggplot2::ggplot(df,ggplot2::aes(db))+ggplot2::geom_line(ggplot2::aes(y = ber))+ggplot2::scale_y_log10(limits = c(min(df$ber) / 2, max(df$ber) * 2))+ggplot2::xlab("Signal Rausch Verh\u00e4ltnis [dB]")+ggplot2::ylab("Bitfehlerrate")
}

```

## Statistik

Bitefehlerrate:

```{r qplot, echo=FALSE, message=FALSE}
summary(df$ber)
```
