---
title: "Turbo Kodierer mit Punktierung"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: beamer_presentation
params:
  orig: !r c(1,1,1,0,0,0,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,0,0,0,1,1,1,1,1,1,1,1,1,1,1,1,1,1)
  interl: !r c(2,1,1,0,0,0,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,0,0,0,1,1,1,1,1,1,1,1,1,1,1,1,1,1)
  parity1: !r c(3,1,1,0,0,0,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,0,0,0,1,1,1,1,1,1,1,1,1,1,1,1,1,1)
  parity2: !r c(4,1,1,0,0,0,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,0,0,0,1,1,1,1,1,1,1,1,1,1,1,1,1,1)
  multipl: !r c(5,1,1,0,0,0,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,0,0,0,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,0,0,0,1,1,1,1,1,1,1,1,1,1,1,1,1,1)
  result: !r c(6,1,1,0,0,0,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,0,0,0,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,0,0,0,1,1,1,1,1,1,1,1,1,1,1,1,1,1)
  permutation: !r c(1,2,3,4,5,6,7)
  punctuation: !r matrix(c(1,0,1,1,1,0), nrow = 3)
  encoder: !r list(N=2, M=2, generators=c(5,7), rsc=TRUE, termination=c(0,1,1,0), next.state=matrix(c(0,2,3,1,2,0,1,3), ncol =2), prev.state=matrix(c(0,3,1,2,1,2,0,3,-1,-1,-1,-1), ncol =3), output=matrix(c(0,0,1,1,3,3,2,2), ncol =2))
header-includes:
- \usepackage{tikz}
- \usepackage{pgfplots}
- \usetikzlibrary{arrows,decorations.pathmorphing,backgrounds,positioning,fit,petri,calc}

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r functions}
binVector <- function(n, min.length) {

  result <- integer()
  i <- 0
  while (n != 0) {
    result <- c(n %% 2, result)
    n = n %/% 2
    i <- i + 1
  }

  zeros <- rep(0, times = min.length)

  result <- c(zeros, result)

  return(paste(tail(result,min.length), collapse = ""))
}

decToBin <- function(x) { if (all(x<2)) x else paste(decToBin(x%/%2), x%%2, sep="") }

octalToDec <- function(x) {
  res <- numeric()
  for(j in 1:length(x)) {
  dec <- 0
  i <- 0
    while (x[j] > 0) {
      dec <- dec + (x[j] %% 10) * (8^i)
      i <- i + 1
      x[j] <- x[j] %/% 10
    }
  res[j] <- dec
  }

  return(res)
}

# returns an ordering of the state numbers for a nice state diagram
ordering <- function(num.states, next.state) {
  #next.state <- matrix(rep(0:(num.states-1), each = 2), ncol = 2)
  result <- integer(1)

  n <- 0
  for (i in 2:num.states) {
    n0 <- next.state[n+1,1]
    n1 <- next.state[n+1,2]

    if (n0 %in% result) {
      n <- n1
    }
    else if (n1 %in% result) {
      n <- n0
    }
    else {
      n <- if (n0 > n1) n0 else n1
    }

    result <- c(result, n)
  }

  return(result)
}

gcd <- function(n, m) {
  if (n == 0 && m == 0) return(0)
  
  n <- abs(n); m <- abs(m)
  if (m > n) {
    t <- n; n <- m; m <- t
  }
  while (m > 0) {
    t <- n
    n <- m
    m <- t %% m
  }
  return(n)
}
```

```{r generatePrintVars, echo=FALSE}
node.short <- 20
node.long <- 45
dots <- function (v, node) if(length(v) > node) ", ..." else ""

if (params$encoder$rsc == TRUE) {
  art.coder <- "Rekursiver"
} else {
  art.coder <- "Nicht-Rekursiver"
}

if (params$encoder$rsc == FALSE) {
  generator.matrix <- 
    paste0(decToBin(octalToDec(params$encoder$generators)), " \\\\ ", collapse = "")
  generator.print <- paste0("(", paste(params$encoder$generators, collapse=","), 
                           ")_8 = \\begin{pmatrix}", generator.matrix, "\\end{pmatrix}")

} else {
  generator.print <- 
    paste0("\\left(1,", 
           paste0("\\frac{", 
              head(params$encoder$generators, length(params$encoder$generators) - 1), "}{",
                        tail(params$encoder$generators, 1), "}", collapse = ","), "\\right)")
}

punctuation.print <- 
    paste0(apply(params$punctuation, 1, function(x) {paste0(x, collapse=" & ")}), collapse = " \\\\ ")
```

## Kodierer Information

- `r art.coder` Kodierer
- Anzahl von Ausgängen : $$N=`r params$encoder$N`$$
- Anzahl von Registern : $$M=`r params$encoder$M`$$
- Generatoren : $$`r generator.print`$$

## Kodierer Matrix : Nächster Zustand
```{r, results='asis'}
next.table <- params$encoder$next.state
colnames(next.table) <- c("Bit 0", "Bit 1")
row.counter <- rep(0:(dim(next.table)[1]-1))
rownames(next.table) <- paste("Zustand ", row.counter)
knitr::kable(next.table, align="c")
```

## Kodierer Matrix : Ausgangsbits
```{r, results='asis'}
output.table <- params$encoder$output
output.table <- matrix(decToBin(as.vector(output.table)), ncol = ncol(output.table))
colnames(output.table) <- c("Bit 0", "Bit 1")
row.counter <- rep(0:(dim(next.table)[1]-1))
rownames(output.table) <- paste("Zustand ", row.counter)
knitr::kable(output.table, align="c")
```

## Kodierer Matrix : Zustandsdiagramm
```{r}
num.states <- 2^params$encoder$M

state.order <- ordering(num.states, params$encoder$next.state)

## STATE DIAGRAM
tikz.diagram <- ""
# state diagram nodes
for (s in 0:(num.states-1)) {
  xpos <- 2.5*sin(s*2*pi/num.states)
  ypos <- 2.5*cos(s*2*pi/num.states)
  position <- paste0(xpos,",",ypos)
  name <- paste(binVector(state.order[s+1], params$encoder$M),collapse = "")
  state <- paste0("\\node[state] (state",state.order[s+1],") at (",position,") {",name,"};")

  tikz.diagram <- paste(tikz.diagram, state)
}

# state diagram connections
for (s in 0:(num.states-1)) {
  this.state <- paste0("(state",s,")")
  n_next.state.0 <- params$encoder$next.state[s+1,1]
  n_next.state.1 <- params$encoder$next.state[s+1,2]
  str_next.state.0 <- paste0("(state",n_next.state.0,")")
  str_next.state.1 <- paste0("(state",n_next.state.1,")")

  label.value.0 <- paste(binVector(params$encoder$output[s+1,1],params$encoder$N),collapse = "")
  label.value.1 <- paste(binVector(params$encoder$output[s+1,2],params$encoder$N),collapse = "")

  # indices of the states in the ordering vector (1 based)
  this.ordering.index <- which(state.order == s)
  next.0.ordering.index <- which(state.order == n_next.state.0)
  next.1.ordering.index <- which(state.order == n_next.state.1)

  # if edges do not go to neighbour, set label near start
  # to avoid label crossings
  near.0 <- ""
  near.1 <- ""
  distance.to.0 <- abs(this.ordering.index - next.0.ordering.index)
  distance.to.1 <- abs(this.ordering.index - next.1.ordering.index)
  if (distance.to.0 > 1 && distance.to.0 < num.states-1) {
    near.0 <- ",near start"
  }

  if (distance.to.1 > 1 && distance.to.1 < num.states-1) {
    near.1 <- ",near start"
  }
  # 2nd check in previous if clause necessary because if state numbers
  # are in first and last position of the ordering, they have distance
  # num.states-1 but are neighbours in the state diagram

  label.0 <- paste0("node [sloped, above",near.0,"] {",label.value.0,"}")
  label.1 <- paste0("node [sloped, above",near.1,"] {",label.value.1,"}")

  # in case of a loop
  angle <- (90-(this.ordering.index-1)*360/num.states) %% 360
  angle.out <- (angle + 15) %% 360
  angle.in <- (angle - 15) %% 360

  if (n_next.state.0 == s) {
    # loop with input bit 0
    loop <- paste0("[looseness=8,out=",angle.out,",in=",angle.in,"]")

    if (sin(angle*pi/180) < 0) {
      label.0 <- paste0("node [sloped, below",near.0,"] {",label.value.0,"}")
    }

    edge.0 <- paste("\\draw[->]",this.state,"to",loop,label.0,this.state,";")
  }
  else {
    # 'normal' edge to other node
    bend <- ""
    if (params$encoder$next.state[n_next.state.0+1,1] == s || params$encoder$next.state[n_next.state.0+1,2] == s) {
      # there is a connection back -> bend the edge
      bend <- "[bend left=15]"
    }
    edge.0 <- paste("\\draw[->]",this.state,"to",bend,label.0,str_next.state.0,";")
  }

  if (n_next.state.1 == s) {
    # loop with input bit 1
    loop <- paste0("[looseness=8,out=",angle.out,",in=",angle.in,"]")

    if (sin(angle*pi/180) < 0) {
      label.1 <- paste0("node [sloped, below",near.1,"] {",label.value.1,"}")
    }

    edge.1 <- paste("\\draw[->, dashed]",this.state,"to",loop,label.1,this.state,";")
  }
  else {
    # 'normal' edge to other node
    bend <- ""
    if (params$encoder$next.state[n_next.state.1+1,1] == s || params$encoder$next.state[n_next.state.1+1,2] == s) {
      # there is a connection back -> bend the edge
      bend <- "[bend left=15]"
    }
    edge.1 <- paste("\\draw[->, dashed]",this.state,"to",bend,label.1,str_next.state.1,";")
  }

  tikz.diagram <- paste(tikz.diagram, edge.0, edge.1)
}
```

\begin{center}
\begin{tikzpicture}[>=stealth, font=\scriptsize]
\tikzstyle{state} = [draw, circle, inner sep=1mm, minimum size=8mm, font=\footnotesize]

`r tikz.diagram`

\end{tikzpicture}
\end{center}

## Turbo-Kodierer Information

- Interleaver : (`r head(params$permutation, node.long)``r dots(params$permutation, node.long)`)
```{r}
  gcd.value <- gcd(length(params$punctuation), sum(params$punctuation) * 3)
```
- Kode-Rate : $$\frac{`r length(params$punctuation) / gcd.value`}{`r sum(params$punctuation) * 3 / gcd.value`}$$
- Punktierungs-Matrix : $$\begin{pmatrix}  `r punctuation.print`  \end{pmatrix}$$

## Turbo-Kodierer mit Punktierung

- Input : `r head(params$orig, node.short)``r dots(params$orig, node.short)`

\begin{center}
\begin{tikzpicture}[node distance=8mm, inner sep=2mm, outer sep=0, >=stealth, font=\footnotesize, align=center]

\tikzstyle{encoderStyle} = [rectangle, draw, minimum height=height("Inp")+4mm]
\tikzstyle{interleaverStyle} = [encoderStyle]
\tikzstyle{startEndStyle} = [encoderStyle]
\tikzstyle{punctureStyle} = [encoderStyle]
\tikzstyle{multiplexerStyle} = [encoderStyle]
\tikzstyle{showStyle} = [rectangle, draw, thick, draw=red, text=red, inner sep=1.5mm]
\tikzstyle{arrowStyle} = [->]
\tikzstyle{showDrawStyle} = [->, red, thick]

\node [interleaverStyle] (interleaver) {Interleaver};
\node [encoderStyle] (encoder1) [above right=of interleaver] {Kodierer 1};
\node [encoderStyle] (encoder2) [below right=of interleaver] {Kodierer 2};
\node [] (multiplexerTemp) [right=of encoder1] {};
\node [multiplexerStyle, rotate=90] (multiplexer) at (multiplexerTemp.east) {Multiplexer};
\node [startEndStyle] (start) [above left=of interleaver] {Input};
\node [] (punctureTemp) [right=of multiplexerTemp] {};
\node [punctureStyle, rotate=90] (puncture) at (punctureTemp.east) {Punktierung};
\node [startEndStyle] (end) [right=of punctureTemp] {Output};

\draw [arrowStyle] (interleaver.south) |- node (afterInterleaver) {}(encoder2.west);
\draw [arrowStyle] (encoder1.east) -- node (afterParity1) {} (multiplexer.north);
\draw [arrowStyle] (start.east)  -| node[midway] (afterInput) {} (interleaver.north);
\draw [arrowStyle] (afterInput.center) |- (encoder1.west);
\draw [arrowStyle] (encoder2.east) -| ++(0.2,0.7) node (afterParity2) {} |- ($(multiplexer.north)+(0,-.5)$);
\draw [arrowStyle] (afterInput.center) |- ($(multiplexer.north)+(0,.5)$);
\draw [arrowStyle] (multiplexer.south) -- node (afterMultiplexer) {} (puncture.north);
\draw [arrowStyle] (puncture.south) -- node (afterPuncture) {}(end.west);

\begin{scope}[on background layer]
\node [draw, fit=(encoder1) (interleaver) (encoder2) (multiplexer) (puncture)] (background) {};
\end{scope}

\visible<2>{
  \node [showStyle] (showAbove) [above=3mm of background] {\textbf{`r head(params$orig, node.short)``r dots(params$orig, node.short)`}};
  \draw [showDrawStyle] (showAbove) -- (afterInput.center);
  \node [showStyle] (showBelow) [below=3mm of background] {\textbf{`r head(params$parity1, node.short)``r dots(params$parity1, node.short)`}};
  \draw [showDrawStyle] (showBelow) -- (afterParity1.center);
  }
\visible<3>{
  \node [showStyle] (showAbove) [above=3mm of background] {\textbf{`r head(params$orig, node.short)``r dots(params$orig, node.short)`}};
  \draw [showDrawStyle] (showAbove) -- (afterInput.center);
  \node [showStyle] (showBelow) [below=3mm of background] {\textbf{`r head(params$interl, node.short)``r dots(params$interl, node.short)`}};
  \draw [showDrawStyle] (showBelow) -- (afterInterleaver.center);
  }
\visible<4>{
  \node [showStyle] (showAbove) [above=3mm of background] {\textbf{`r head(params$parity2, node.short)``r dots(params$parity2, node.short)`}};
  \draw [showDrawStyle] (showAbove) -- (afterParity2.center);
  \node [showStyle] (showBelow) [below=3mm of background] {\textbf{`r head(params$interl, node.short)``r dots(params$interl, node.short)`}};
  \draw [showDrawStyle] (showBelow) -- (afterInterleaver.center);
  }
\visible<5>{
  \node [showStyle] (show) [above=3mm of background] {\textbf{`r head(params$multipl, node.short)``r dots(params$multipl, node.short)`}};
  \draw [showDrawStyle] (show) -- (afterMultiplexer.center);
  \node [showStyle] (showBelow) [below=3mm of background] {\textbf{`r head(params$result, node.short)``r dots(params$result, node.short)`}};
  \draw [showDrawStyle] (showBelow) -- (afterPuncture.center);
  }

\end{tikzpicture}
\end{center}

- Output : `r head(params$result, node.long)``r dots(params$result, node.long)`
